The evolution of badges of status with learners

### 2019-08-15 QD_report.Rmd
New graph in the QD report

# How do learners fare against the "pure" strategies

@@

>>>>

# How do learners fare against the "pure" strategies?

@@

# How do learners behave when signals are honest?

```{r fig9, echo=FALSE,fig.cap="\\label{fig:honest_learn}Actor and critic developed when signals are honest. Left panel: honest signal. Right panel: learners behavioral response ",out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations//learHonest_//QualStDv_//weightsVarQualSt.png")

```

### 2019-08-15 QD_report.tex
New graph in the QD report

\hypertarget{how-do-learners-fare-against-the-pure-strategies}{%
\section{How do learners fare against the ``pure''
strategies}\label{how-do-learners-fare-against-the-pure-strategies}}

@@

>>>>

\hypertarget{how-do-learners-fare-against-the-pure-strategies}{%
\section{How do learners fare against the ``pure''
strategies?}\label{how-do-learners-fare-against-the-pure-strategies}}

@@

\hypertarget{how-do-learners-behave-when-signals-are-honest}{%
\section{How do learners behave when signals are
honest?}\label{how-do-learners-behave-when-signals-are-honest}}

\begin{figure}
\includegraphics[width=1\linewidth]{Simulations//learHonest_//QualStDv_//weightsVarQualSt} \caption{\label{fig:honest_learn}Actor and critic developed when signals are honest. Left panel: honest signal. Right panel: learners behavioral response }\label{fig:fig9}
\end{figure}
